Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-15 R/model_persistence_markdown.Rmd
Update

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""), col_types =
    cols(
      .default = "?",
      plot = "f",
      site = "f",
      sand_ratio = "f",
      substrate_depth = "f",
      target_type = col_factor(levels = c(
        "dry_grassland", "hay_meadow"
      )),
      seed_density = "f",
      exposition = col_factor(levels = c(
        "north", "south"
      )),
      survey_year = "c"
    )
  ) %>%
  ### Exclude data of seed mixtures
  filter(survey_year != "seeded") %>%
  pivot_longer(cols = c(B, C), names_to = "index", values_to = "n",
               names_transform = as.factor) %>%
  filter(index == "B" & presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    id = factor(id)
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, n
  )
```

@@

```{r}
load(file = here("data", "processed", "model_persistence_1.Rdata"))
load(file = here("data", "processed", "model_persistence_2.Rdata"))
load(file = here("data", "processed", "model_persistence_3.Rdata"))
```

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
```

@@

```{r}
prior_summary(m_1, all = FALSE)
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

>>>>

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_temporal.csv"),
  col_names = TRUE, na = c("na", "NA", ""), col_types =
    cols(
      .default = "?",
      plot = "f",
      site = "f",
      sand_ratio = "f",
      substrate_depth = "f",
      target_type = col_factor(levels = c(
        "dry_grassland", "hay_meadow"
      )),
      seed_density = "f",
      exposition = col_factor(levels = c(
        "north", "south"
      )),
      survey_year = "c"
    )
  ) %>%
  ### Exclude data of seed mixtures
  filter(presabu == "presence") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    id = factor(id),
    n = persistence
  ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, n
  )
```

@@

```{r}
load(file = here("outputs", "models", "model_persistence_1.Rdata"))
load(file = here("outputs", "models", "model_persistence_3.Rdata"))
```

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot))
```

@@

```{r}
prior_summary(m_1, all = FALSE)
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```
